Using Sweat Na/Cl Ratio to Predict CFTR-RD and CRMS

### 2024-03-21 Edith Zemanick/Sweat Test/sweat_test_cf_conference.qmd
method descriptions done

---
title: "Using Sweat Na/Cl Ratio to Predict CFTR-RD or CRMS"
author: "Tim Vigers"
date: "today"
date-format: long
format: revealjs
editor: source
bibliography: Presentation.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
---

@@

Detail here

@@

Detail here

@@

>>>>

---
title: "Using Sweat Na/Cl Ratio to Predict CFTR-RD and CRMS"
author: "Tim Vigers"
date: "today"
date-format: long
format: revealjs
editor: source
bibliography: Presentation.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
---

@@

- An approach to splitting up a data set into K non-overlapping groups.

- We want the within-cluster variation to be as low as possible.

- There are several metrics for within-cluster variation, but we usually use the squared Euclidean distance between all pairs of points in a given cluster divided by the number of points in the cluster.

## The K-means clustering algorithm

1. Randomly assign each observation to clusters 1 through K.

2. Iterate until the cluster assignments stop changing:

  a. For each cluster, compute the cluster centroid (a vector of feature means).

  b. Re-assign each point to the cluster corresponding with the closest centroid.

## The K-means clustering algorithm

![](kmeans.jpg)

@@

- Essentially, a regression tree is a way of predicting which category an observation will fall into based on a series of data splitting rules.

- We want to split the predictor space (the set of possible values for the variables we're interested in) into $R_1, R_2, ... R_J$ non-overlapping regions that minimize some measure of model predictive value (RSS, error rate, etc.).

- Because in most cases it's impossible to look at every single partition of the predictor space, we use a top-down and greedy approach to splitting up the data.

  - This is a fancy way of saying that we use the data split that gives us the best result at a given step, and don't look at future steps.

## Potential issues

- This kind of recursive splitting can results in trees that predict extremely well with the training data but are not generalizable.

- To avoid this we essentially build one large, overfit tree, and then "prune" it down to its best subtree.

  - Won't go into detail here, but the process is called *cost complexity pruning* and also utilizes cross validation to approximate the test error.

## Baseball example

![](hitters.jpg)

@@

# Random forests
